\documentclass[10pt]{extarticle}

\usepackage{fullpage}
\usepackage{enumitem}
\usepackage{subcaption}

% language and encoding
\usepackage{polski}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}

% metadata and link styling
\usepackage[
  pdfauthor={Ekre Ceannmor},
  pdftitle={WMA Zero Exam},
  pdfkeywords={},
  pdfproducer={Latex with hyperref},
  pdfcreator={tectonic},
  colorlinks=true,
  allcolors=MidnightBlue
]{hyperref}

% colours
\usepackage[svgnames, table]{xcolor}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}

% footnotes in tables and figures
\usepackage{tablefootnote}
\usepackage{threeparttable}

% [H] specifier
\usepackage{float}

% specifying landscape mode for a page
\usepackage{pdflscape}

% external graphics
\usepackage{graphicx}
\graphicspath{ {./resources/} }

% table of contents styling
\usepackage[nottoc]{tocbibind}
\settocbibname{References}
\setcounter{tocdepth}{5}

\usepackage{bookmark}

% layout
\topmargin = -1.5cm
\textheight = 24cm

% block highlighting
\usepackage[framemethod=tikz]{mdframed}

% pretty tables
\usepackage{booktabs}

\usepackage[symbol*]{footmisc}
\setfnsymbol{wiley}

\pagenumbering{gobble}

% https://tex.stackexchange.com/questions/177202/booktabs-and-row-color
\colorlet{tableheadcolor}{gray!25} % Table header colour = 25% gray
\newcommand{\headcol}{\rowcolor{tableheadcolor}} %he
\colorlet{tablerowcolor}{gray!10} % Table row separator colour = 10% gray
\newcommand{\rowcol}{\rowcolor{tablerowcolor}} %
% Command \topline consists of a (slightly modified) \toprule followed by a \heavyrule rule of colour tableheadcolor (hence, 2 separate rules)
\newcommand{\topline}{\arrayrulecolor{black}\specialrule{0.1em}{\abovetopsep}{0.5pt}%
  \arrayrulecolor{tableheadcolor}\specialrule{\belowrulesep}{0pt}{-3pt}%
  \arrayrulecolor{black}
}
% Command \midline consists of 3 rules (top colour tableheadcolor, middle colour black, bottom colour white)
\newcommand{\midline}{\arrayrulecolor{tableheadcolor}\specialrule{\aboverulesep}{-1pt}{0pt}%
  \arrayrulecolor{black}\specialrule{\lightrulewidth}{0pt}{0pt}%
  \arrayrulecolor{white}\specialrule{\belowrulesep}{0pt}{-3pt}%
  \arrayrulecolor{black}
}
% Command \rowmidlinecw consists of 3 rules (top colour tablerowcolor, middle colour black, bottom colour white)
\newcommand{\rowmidlinecw}{\arrayrulecolor{tablerowcolor}\specialrule{\aboverulesep}{0pt}{0pt}%
  \arrayrulecolor{black}\specialrule{\lightrulewidth}{0pt}{0pt}%
  \arrayrulecolor{white}\specialrule{\belowrulesep}{0pt}{0pt}%
\arrayrulecolor{black}}
% Command \rowmidlinewc consists of 3 rules (top colour white, middle colour black, bottom colour tablerowcolor)
\newcommand{\rowmidlinewc}{\arrayrulecolor{white}\specialrule{\aboverulesep}{0pt}{0pt}%
  \arrayrulecolor{black}\specialrule{\lightrulewidth}{0pt}{0pt}%
  \arrayrulecolor{tablerowcolor}\specialrule{\belowrulesep}{0pt}{0pt}%
\arrayrulecolor{black}}
% Command \rowmidlinew consists of 1 white rule
\newcommand{\rowmidlinew}{\arrayrulecolor{white}\specialrule{\aboverulesep}{0pt}{0pt}%
\arrayrulecolor{black}}
% Command \rowmidlinec consists of 1 tablerowcolor rule
\newcommand{\rowmidlinec}{\arrayrulecolor{tablerowcolor}\specialrule{\aboverulesep}{0pt}{0pt}%
\arrayrulecolor{black}}
% Command \bottomline consists of 2 rules (top colour)
\newcommand{\bottomline}{\arrayrulecolor{white}\specialrule{\aboverulesep}{0pt}{-2pt}%
\arrayrulecolor{black}\specialrule{\heavyrulewidth}{0pt}{\belowbottomsep}}%
\newcommand{\bottomlinec}{\arrayrulecolor{tablerowcolor}\specialrule{\aboverulesep}{0pt}{0pt}%
\arrayrulecolor{black}\specialrule{\heavyrulewidth}{0pt}{\belowbottomsep}}%

\newcommand{\varQuad}[1]{\hskip#1em\relax}

% Code blocks
\usepackage{listings}
\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\lstdefinestyle{default}{
  commentstyle=\color{codegreen},
  numberstyle=\tiny\color{codegray},
  stringstyle=\color{codepurple},
  basicstyle=\footnotesize\ttfamily,
  keywordstyle=\bfseries\color{magenta},
  backgroundcolor=\color{gray!10!white},
  breakatwhitespace=false,
  breaklines=true,
  keepspaces=true,
  numbers=left,
  numbersep=5pt,
  showspaces=false,
  showstringspaces=false,
  showtabs=false,
  tabsize=2,
  %=!=!=!=!=!=!=!=!=
  language=Python,
  %=!=!=!=!=!=!=!=!=
  frame=tb
}
\lstset{style=default}

% More tightly-packed text
\usepackage{setspace}

% Better indentation control
\usepackage{parskip}

\newcommand{\titletext}{Zero exam}
\newcommand{\subtitletext}{}

\usepackage{multicol}

%===============================================================================
\begin{document}

{\Large \textbf{\titletext}} \\
% {\large \subtitletext} \\

%===============================================================================
\section*{Rules and exam form}
If you have submitted and obtained a positive grade from all projects, you can take the zero-term exam (kolokwium).
The exam has to be taken during normal class hours at any point during the semester, provided the above condition is met.
Please notify the instructor at least 3 days in advance.

You will find a list of potential questions below, you can expect to receive up to 5 questions (at random) from the list as your exam task.
The exam is written, you will have 1.5h (one class) to answer the given questions and provide explanations to your answers.
You are free to draw graphs to help explain your answer.

No extra resources are allowed during the exam (cheatsheets, lecture notes, own notes, internet, etc).

%===============================================================================
\section*{Question pool}

\begin{multicols*}{2}
\begin{enumerate}
    \item List as many image distortion types as you can. Describe 2.
    \item Explain the (main) steps of edge detection.
    \item Explain the concept of image segmentation.
    \item Describe the CMYK and HSV colour models.
    \item Explain the functioning of a convolution layer.
    \item Describe the concept of object detection.
    \item Compare supervised and semi-supervised learning.
    \item List as many basic morphological operations as you can. Describe 2.
    \item Explain the (main) steps of corner detection.
    \item List the geometric primitives used in computer graphics.
    \item \dots
\end{enumerate}
\end{multicols*}

\end{document}